\section{Getting the tweet}
\subsection{Tweet Streamer}
Using the Streaming API, the Tweet Streamer is responsible to get the brand new tweets, not yet indexed by the Search API. Due to the limit of 1\%, the amount of tweets that might be found in both searches is small, but will still have to be considered. The amount of interesting data from the Streamer might be smaller, as we cannot ask the API to filter directly for both keywords and localization. We can only have a few streams by connection. So to compute interesting tweets, we launch one stream on the Tweet Streamer with all the location parameters. We do this because we only can launch few streams. Because the number of location parameters is limited to 20, we will also merge the location parameters that are close to each other, i.e. the squares. We will thus receive a lot of tweets in some kind of disorder.

This is typically a Big Data issue, we receive unparsed data from different sources that we need to put in the same format. In this case, we have one listener per word and per square, and we have a lot of data that is comming that will fit at least one square, but that will not contain a desired word in most of the cases.

From the received tweets, we look locally at their location parameter and the words they contain, search from this for their correct listener, and send the tweet. We will receive a lot of data, and lot's of tweets that are in the desired location but do not contain the keywords we are interested in. To be able to rapidly discard non relevant tweet, each time the Tweet Streamer receives a ping, he will discard all the non relevant tweets in his InputStream until he finds a correct one to return. A correct tweet is a tweet containing one of the desired keywords, because we already know that they will be in one of the desired squares, because we specified it in the parameters.
